Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-09 Response to reviewers - r2.tex

\begin{verbatim}
This reviewer would also suggest to provide more details on 
security aspect of the system. Some hints are provided in 
previous comments. Additionally, as the client/server 
interaction is concerned, what measures and aspects have 
been applied in order to identify and prevent malicious 
parties to manipulate or inject malicious rules in the system? 
By injecting such rules, the complete sub-network of clients 
of the company can be affected. Furthermore, author assumes 
that the clients are non-rooted devices. What happens, and at 
which extent can some rooted device affect local application 
of the system, and also central server and other clients?
\end{verbatim}

\textcolor{blue}{TODO}

\begin{verbatim}
For the section 5 and discussion, this reviewer would suggest to
consider providing overview in the form of table(s) or figure,
comparing different aspects of MUSES and other tools and providing
hints/references to further details in this or other works. As there
are many features of MUSES and other tools, employed approaches and
techniques, different coverages and limitations, such overview could
contribute to clarity and position of the proposed solution. 
\end{verbatim}

We agree with the reviewer. Two comparative tables have been included in
section 5 (Table 1 and Table 2). They summarize some of the features of
the presented tools and MUSES regarding the taxonomy we have described in the paper (Section 3); and also their features with respect to licenses, devices and prices.
As it can be seen, MUSES is the most complete considering Table 1. Moreover, having a look at Table 2, all the other systems are proprietary and have a cost, which makes MUSES unique in the sense that, being free software, can be adapted and extended by corporate security departments to the corporate special needs.

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Cambios en las tablas y en las respuestas

% Antonio - pongo esto en una sección nueva para que destaque más. Es muy importante para los revisores. Por favor Paloma, revisa si lo que he puesto es correcto (número de usuarios y demás).
\subsubsection{Trials and tests of MUSES}

@@

\begin{table}[ht]

  \centering
  \renewcommand{\arraystretch}{1.8}% Spread rows out...
  \resizebox{12cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering\arraybackslash}m{0.8in}}
    \toprule
      & \textbf{Offline threat detection method} & \textbf{Updatable database} & \textbf{Standalone} & \textbf{Non-invasive data access} & \textbf{Superuser system control} \\
    \midrule
    MUSES & \cmark & \cmark & \cmark & \cmark & \cmark  \\
     \arrayrulecolor[gray]{0.8}\hline
    IBM Mobile Security & \xmark & \xmark & \cmark & \xmark & \xmark  \\
     \arrayrulecolor[gray]{0.8}\hline
    Sophos Mobile Control & \cmark & \xmark & \cmark & \xmark & \xmark \\
     \arrayrulecolor[gray]{0.8}\hline
    Samsung Knox & \cmark & \nmark & \cmark & \nmark & \cmark\\
     \arrayrulecolor[gray]{0.8}\hline
     Blackbery Balance & \nmark & \nmark & \cmark & \nmark & \cmark\\
     \arrayrulecolor[gray]{0.8}\hline
    Blackphone & \nmark & \nmark & \cmark & \cmark & \nmark\\
     \arrayrulecolor[gray]{0.8}\hline
    Android for Work & \xmark & \xmark & \cmark & \xmark & \cmark\\
    \bottomrule
  \end{tabular}
  }
  \caption{Proposed taxonomy to classify the BYOD tools described in this paper.}
  \label{tab:taxonomy}
\end{table}

\begin{table}[ht]

  \centering
  \renewcommand{\arraystretch}{1.8}% Spread rows out...
%  \resizebox{8cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
       \toprule
      & \textbf{License} & \textbf{Devices} & \textbf{Price} \\
       \midrule
    MUSES & OpenSource &  & Free*  \\
       \arrayrulecolor[gray]{0.8}\hline
    IBM Mobile Security & Proprietary & IOS, Android, Windows Phone, Blackberry  &  By Request\\\\
        \arrayrulecolor[gray]{0.8}\hline
    Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
        \arrayrulecolor[gray]{0.8}\hline
    Samsung Knox and Blackbery Balance & Proprietary & Android Samsung Devices and IOS & 12\$ per year/device \\
        \arrayrulecolor[gray]{0.8}\hline
    Blackphone & Proprietary & Own device & 120\$ per year \\
        \arrayrulecolor[gray]{0.8}\hline
    Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\
       \bottomrule
  \end{tabular}
%  }
  \caption{Features of the analyzed products considering licenses, type of devices and price.}
  \label{tab:features}
\end{table}
% Antonio - Antares, ¿no había más tablas?
% Por favor, que alguien rellene los datos de la solución de IBM. ¿Fergu?¿Antares?
% Quizá habría que indicar que MUSES se puede instalar en PC también en la tabla. ¿Sabéis si los demás se puede o son sólo para smartphones/tablets?

>>>>

% ---------------------------------------------------

% Antonio - pongo esto en una sección nueva para que destaque más. Es muy importante para los revisores. Por favor Paloma, revisa si lo que he puesto es correcto (número de usuarios y demás).
\subsection{Trials and tests of MUSES}
\label{subsec:trials}

@@

\begin{table}[ht]
\begin{footnotesize}
  \centering
  \renewcommand{\arraystretch}{2.0}% Spread rows out...
%  \resizebox{12cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering\arraybackslash}m{0.6in}}
    \toprule
      & \textbf{Offline threat detection method} & \textbf{Updatable database} & \textbf{Standalone} & \textbf{Non-invasive data access} & \textbf{Superuser system control} \\
    \midrule
    MUSES & \cmark & \cmark & \cmark & \cmark & \cmark  \\
     \arrayrulecolor[gray]{0.6}\hline
    IBM Mobile Security & \xmark & \xmark & \cmark & \xmark & \xmark  \\
     \arrayrulecolor[gray]{0.6}\hline
    Sophos Mobile Control & \cmark & \xmark & \cmark & \xmark & \xmark \\
     \arrayrulecolor[gray]{0.6}\hline
    Samsung Knox & \cmark & \nmark & \cmark & \nmark & \cmark\\
     \arrayrulecolor[gray]{0.6}\hline
     Blackbery Balance & \nmark & \nmark & \cmark & \nmark & \cmark\\
     \arrayrulecolor[gray]{0.6}\hline
    Blackphone & \nmark & \nmark & \cmark & \cmark & \nmark\\
     \arrayrulecolor[gray]{0.6}\hline
    Android for Work & \xmark & \xmark & \cmark & \xmark & \cmark\\
    \bottomrule
  \end{tabular}
%  }
\end{footnotesize}
  \caption{Features of the analyzed tools regarding the proposed taxonomy to classify BYOD systems (see Section \ref{sec:toolsreview}).}
  \label{tab:taxonomy}
\end{table}

\begin{table}[ht]
\begin{footnotesize}
  \centering
  \renewcommand{\arraystretch}{1.8}% Spread rows out...
%  \resizebox{8cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
       \toprule
      & \textbf{License} & \textbf{Devices} & \textbf{Price} \\
       \midrule
    MUSES & OpenSource &  & Free  \\
       \arrayrulecolor[gray]{0.8}\hline
    IBM Mobile Security & Proprietary & IOS, Android, Windows Phone, Blackberry  &  By Request\\\\
        \arrayrulecolor[gray]{0.8}\hline
    Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
        \arrayrulecolor[gray]{0.8}\hline
    Samsung Knox and Blackbery Balance & Proprietary & Android Samsung Devices and IOS & 12\$ per year/device \\
        \arrayrulecolor[gray]{0.8}\hline
    Blackphone & Proprietary & Own device & 120\$ per year \\
        \arrayrulecolor[gray]{0.8}\hline
    Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\
       \bottomrule
  \end{tabular}
%  }
\end{footnotesize}
  \caption{Features of the analyzed products considering licenses, type of devices and price.}
  \label{tab:features}
\end{table}
% Antonio - Antares, ¿no había más tablas?
% Por favor, que alguien rellene los datos de la solución de IBM. ¿Fergu?¿Antares?
% Quizá habría que indicar que MUSES se puede instalar en PC también en la tabla. ¿Sabéis si los demás se puede o son sólo para smartphones/tablets?
